### 2017-08-01 README.Rmd
add note that visdat is on CRAN, add the rOpenSci footer :tada:

```{r installation, eval = FALSE}
# install.packages("devtools")

devtools::install_github("njtierney/visdat")
```

@@

>>>>

visdat is available on CRAN

```{r install-cran, eval = FALSE}

install.packages("visdat")

If you would like to use the development version, install from github with:

```{r installation, eval = FALSE}

# install.packages("devtools")
devtools::install_github("ropensci/visdat")
```

@@

[![ropensci_footer](https://ropensci.org/public_images/ropensci_footer.png)](https://ropensci.org)
